---
output: github_document
---

# bbr: basketball-reference data in R

[![Travis-CI Build Status](https://travis-ci.org/mbjoseph/bbr.svg?branch=master)](https://travis-ci.org/mbjoseph/bbr) 
[![Coverage Status](https://img.shields.io/codecov/c/github/mbjoseph/bbr/master.svg)](https://codecov.io/github/mbjoseph/bbr?branch=master)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/bbr)](https://cran.r-project.org/package=bbr)
[![Licence](https://img.shields.io/badge/licence-GPL--3-blue.svg)](https://www.gnu.org/licenses/old-licenses/gpl-3.0.html)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-brightgreen.svg)](/commits/master)

<!-- README.md is generated from README.Rmd. Please edit that file -->

The bbr package is designed to quickly fetch tidy data from www.basketball-reference.com. 
This package is actively under development and the interface will change as new features are added.

## Installation

```{r, eval = FALSE}
devtools::install_github("mbjoseph/bbr")
```

## Example usage

The `get_season` function retrieves season summary data for one season. 

```{r, echo = TRUE}
library(bbr)

ninetyone <- get_season(1991)
str(ninetyone)
```

The `get_players` function gets player data for individuals by last initial.

```{r, echo = TRUE}
a_data <- get_players("A")
str(a_data)
```
